\documentclass{GEWISDocument}

\title{Example title}
\subtitle{Example subtitle}
\footer{Example footer}

\renewcommand*{\HyperDestNameFilter}[1]{%
\jobname-\HyperDestLabelReplace{#1}%
}

\hyphenation{ëe-ee}

\begin{document}
\faHandPointerO

Shë asked the question even though she didn't really want to hear the answer. It was a no-win situation since she already knew. If he told the truth, she'd get confirmation of her worst fears. If he lied, she'd know that he wasn't who she thought he was which would be almost as bad. Yet she asked the question anyway and waited for his answer.
She tried to explain that love wasn't like pie. There wasn't a set number of slices to be given out. There wasn't less to be given to one person if you wanted to give more to another. That after a set amount was given out it would all disappear. She tried to explain this, but it fell on deaf ears.

The amber droplet hung from the branch, reaching fullness and ready to drop. It waited. While many of the other droplets were satisfied to form as big as they could and release, this droplet had other plans. It wanted to be part of history. It wanted to be remembered long after all the other droplets had dissolved into history. So it waited for the perfect specimen to fly by to trap and capture that it hoped would eventually be discovered hundreds of years in the future.

His parents continued to question him. He didn't know what to say to them since they refused to believe the truth. He explained again and again, and they dismissed his explanation as a figment of his imagination. There was no way that grandpa, who had been dead for five years, could have told him where the treasure had been hidden. Of course, it didn't help that grandpa was roaring with laughter in the chair next to him as he tried to explain once again how he'd found it.

She wanted rainbow hair. That's what she told the hairdresser. It should be deep rainbow colors, too. She wasn't interested in pastel rainbow hair. She wanted it deep and vibrant so there was no doubt that she had done this on purpose.

I haven't bailed on writing. Look, I'm generating a random paragraph at this very moment in an attempt to get my writing back on track. I am making an effort. I will start writing consistently again!

The red glint of paint sparkled under the sun. He had dreamed of owning this car since he was ten, and that dream had become a reality less than a year ago. It was his baby and he spent hours caring for it, pampering it, and fondling over it. She knew this all too well, and that's exactly why she had taken a sludge hammer to it.

Pink ponies and purple giraffes roamed the field. Cotton candy grew from the ground as a chocolate river meandered off to the side. What looked like stones in the pasture were actually rock candy. Everything in her dream seemed to be perfect except for the fact that she had no mouth.

It was difficult to explain to them how the diagnosis of certain death had actually given him life. While everyone around him was in tears and upset, he actually felt more at ease. The doctor said it would be less than a year. That gave him a year to live, something he'd failed to do with his daily drudgery of a routine that had passed as life until then.

They rushed out the door, grabbing anything and everything they could think of they might need. There was no time to double-check to make sure they weren't leaving something important behind. Everything was thrown into the car and they sped off. Thirty minutes later they were safe and that was when it dawned on them that they had forgotten the most important thing of all.

Pink ponies and purple giraffes roamed the field. Cotton candy grew from the ground as a chocolate river meandered off to the side. What looked like stones in the pasture were actually rock candy. Everything in her dream seemed to be perfect except for the fact that she had no mouth.

It was difficult to explain to them how the diagnosis of certain death had actually given him life. While everyone around him was in tears and upset, he actually felt more at ease. The doctor said it would be less than a year. That gave him a year to live, something he'd failed to do with his daily drudgery of a routine that had passed as life until then.

They rushed out the door, grabbing anything and everything they could think of they might need. There was no time to double-check to make sure they weren't leaving something important behind. Everything was thrown into the car and they sped off. Thirty minutes later they were safe and that was when it dawned on them that they had forgotten the most important thing of all.
\end{document}